---
title: "Expedia Data Retrieval"
output: html_notebook
---

This notebook details the retrieval of hotel and destination data from Expedia. The actual collection of data was mostly scraped externally (by listening in Network for a response file in Chrome's Developer tools). Other web scrapers may be used, but should take note that the response should be a JSON object format.

In this case, the response was recorded for each new batch of 50 hotels when the "See More" button was clicked on a search query for hotels in Tokyo, then their responses copied into a text editor, saved as .json files, and all collated in a zipped folder. The default path to look at is /data/Hotels/Expedia_hotels.zip

The code below will extract information from all these files and turn them into tibbles for easy usage.

```{r Get hotels, eval=F}
#NEW search condition: 6 - 7 November 2019, 1 adult 1 room.

get_hotels = function(path) {
  test = read_json(path)$hotels %>% keep(~.x$type == "HotelViewModel")
  test_tibble = tibble(hotelId = map(test, "hotelId") %>% unlist(),
                       hotelName = map(test, "hotelName") %>% unlist(),
                       #shortlistModel = map(test, "shortlistModel"),
                       displayPrice = map(test, "displayPrice") %>% unlist(),
                       latitude = map(test, "latitude") %>% unlist(),
                       longitude = map(test, "longitude") %>% unlist(),
                       hotelFlags = map(test, "hotelFlags"),
                       price = map(test, "price"),
                       neighborhood = map(test, "neighborhood") %>% unlist(),
                       reviews = map(test, "reviews"),
                       resultType = map(test, "resultType") %>% unlist(),
                       comparisonModel = map(test, "comparisonModel")) %>% 
    drop_na() %>% 
    mutate(price.lead = map(price, "lead") %>% unlist(),
           price.strikeout = map(price, "strikeOut", .default = NA_character_) %>% unlist(),
           reviews.localizedOverallRating = map(reviews, "localizedOverallRating") %>% unlist(),
           reviews.localizedCount = map(reviews, "localizedCount") %>% unlist(),
           reviews.superlative = map(reviews, "superlative", .default = NA_character_) %>% unlist(),
           comparisonModel.amenities = map(comparisonModel, "amenities"),
           comparisonModel.starRating = map(comparisonModel, "starRating") %>% unlist()) %>% 
    mutate(displayPrice = parse_number(displayPrice),
           latitude = parse_number(latitude),
           longitude = parse_number(longitude),
           price.lead = parse_number(price.lead),
           price.strikeout = parse_number(price.strikeout),
           reviews.localizedOverallRating = parse_number(reviews.localizedOverallRating),
           reviews.localizedCount = parse_number(reviews.localizedCount),
           reviews.superlative = parse_factor(reviews.superlative,
                                              levels = c(NA_character_, "Good", "Very Good", "Excellent", "Wonderful", "Exceptional"),
                                              ordered = T)) %>% 
    mutate(price.strikeout = if_else(is.na(price.strikeout), price.lead, price.strikeout)) %>% 
    select(hotelId, 
           hotelName, 
           neighborhood, 
           price.lead, 
           price.strikeout,
           reviews.superlative,
           reviews.localizedOverallRating,
           reviews.localizedCount,
           comparisonModel.starRating,
           latitude,
           longitude,
           hotelFlags, 
           comparisonModel.amenities,
           comparisonModel)

  return(test_tibble)
}

assumedLocation = here::here("data/Hotels/Expedia_hotels.zip")
if(file.exists(assumedLocation)){
  local_path = assumedLocation
} else {
  local_path = choose.files(default = here::here(), caption = "Select zip folder containing Expedia hotel jsons", multi = F)
}

local_path %>% unzip(exdir = here::here("data/Hotels/Expedia_hotels"))
hotels = here::here("data/Hotels/Expedia_hotels") %>% list.files(pattern = "*.json", full.names = T) %>% map(get_hotels) %>% bind_rows()

write_rds(hotels, here::here("data/hotels.rds"))
```

```{r Expedia destinations}
destinations = here::here("data/Hotels/Expedia_hotels") %>% 
  list.files(pattern = "*.json", full.names = T) %>%
  map(read_json) %>% 
  map(c("sortAndFilter", "options", "poi", "options")) %>% 
  unlist(recursive = F) %>%  
  map(as_tibble) %>% 
  bind_rows() %>% 
  separate(value, sep = ":", into = c("value", "extrainfo")) %>% 
  separate(value, sep = ",", into = c("latitude", "longitude")) %>% 
  select(-selected) %>% 
  mutate_at(.vars = 2:4, .funs = as.numeric) %>% 
  distinct()

#so far, iterating over all json responses gives the same 20 destinations. Perhaps they are classified by city.

destinations_sf = destinations %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 6668) %>%
  st_transform(6677)

## Tmap is needed for displaying this
# destinations_sf %>% mutate(colour = case_when(label == "SensÅ-ji Temple" ~ "goldenrod1",
#                                               label == "Asakusa Shrine" ~ "goldenrod1",
#                                               TRUE ~ "maroon")) %>% 
#   tm_shape() +
#   tm_dots(col = "colour") +
#   tm_basemap(server = "OpenStreetMap", alpha = 0.3) +
#   tm_layout(title = "Expedia Destinations")

write_rds(destinations, here::here("data/destinations.rds"))
write_rds(destinations_sf, here::here("data/destinations_sd.rds"))
```
